---
title: "QMSS G5072 Homework 2"
author: "Mengfei Xiao"
date: "October 1st, 2018"
output: 
  html_document:
    keep_md: true
---

```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
library(knitr)
opts_chunk$set(fig.path="images/")
```


## Choose a Data Set
The data we want to use as following: [U.S. Chronic Disease Indicators (CDI)](https://data.cdc.gov/Chronic-Disease-Indicators/U-S-Chronic-Disease-Indicators-CDI-/g4ie-h725).

```{r echo = FALSE, results = 'hide', warning = FALSE, message = FALSE}
# Load the data set
library(readr)
dataset <- read_csv("U.S._Chronic_Disease_Indicators_CDI.csv")
head(dataset)
```


## Selection of Data and Tidying
My idea to solve this question: There are 34 columns in the original excel, but according to the requirements of the question, we only need to keep the columns related to the analysis, so we choose the following columns, and filter the data. We only keep the data related to ***Bing Drinking*** and ***Poverty***.
```{r echo = FALSE, warning = FALSE, message = FALSE}
# Delete the columns we don't need
dataset_selected <- dataset[,which(names(dataset) %in% c("LocationDesc",
                                                         "LocationAbbr",
                                                         "YearEnd",
                                                         "Question",
                                                         "DataValueType",
                                                         "DataValue",
                                                         "StratificationCategory1",
                                                         "Stratification1"))]
```

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Delete the rows we don't need
dataset_selected_row <- dataset_selected[(dataset_selected$Question %in% 
                                        c("Binge drinking prevalence among adults aged >= 18 years", 
                                        "Poverty")) & 
                                        (dataset_selected$DataValueType == "Crude Prevalence"),]

dataset_selected_row <- dataset_selected_row[(dataset_selected_row$Question == "Binge drinking prevalence among adults aged >= 18 years" & 
                                    dataset_selected_row$StratificationCategory1 %in% 
                                    c("Overall", "Gender")) | 
                                    (dataset_selected_row$Question == "Poverty" & 
                                    dataset_selected_row$StratificationCategory1 == "Overall"),]
```

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Format the dataset
library(tidyr)

# Combine two columns
dataset_selected_row$Type <- paste(dataset_selected_row$Question, dataset_selected_row$Stratification1, sep = "-")
dataset_selected_row <- dataset_selected_row[,which(names(dataset_selected_row) %in% 
                                                      c("LocationDesc", 
                                                        "LocationAbbr",
                                                        "YearEnd",
                                                        "Type",
                                                        "DataValue"))]
dataset_reshape <- spread(dataset_selected_row, key = "Type", value = "DataValue")
```

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Rename the dataset
names(dataset_reshape) <- c("year","stateabb", "state", "binge_female", 
                            "binge_male", "binge_all", "poverty")

# Output the dataset
write.csv(dataset_reshape, "binge_clean.csv", row.names = FALSE)
```


## Data Transformation
##### Question 5: Produce a table that shows the overall, female, and male binge drinking prevalences across U.S. States in the most recent year of data for the Top 10 binge drinking states.
```{r echo = FALSE, warning = FALSE, message = FALSE}
library(dplyr)
dataset_2016 <- filter(dataset_reshape, year == 2016)
overall_top10 <- select(arrange(dataset_2016, desc(binge_all)), 
                        "year", "state", "stateabb", "binge_all", "binge_female", "binge_male")[1:10,]
result_top10 <- data.frame(binge_all = overall_top10)
names(result_top10) <- c("year", "state", "stateabb", "binge_all", "binge_female", "binge_male")
```

```{r table, echo = FALSE, warning = FALSE, message = FALSE}
print(result_top10)
```


##### Question 6: Make a simple scatter plot showing the correlation between the overall poverty prevalence in a state and the prevalence of binge drinking in the overall population. Add a loess smoothed fit curve to indicate the pattern. Comment briefly.
My idea to solve this question: Since I cannot accurately say which variable affects another variable or which variable must be the independent variable, therefore I draw two scatter plots respectively with poverty as the independent variable and binge_all as the independent variable.
```{r echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2)
ggplot(data = dataset_reshape[(!is.na(dataset_reshape$binge_all)) & 
                              (!is.na(dataset_reshape$poverty)),], 
                              aes(x = poverty, y = binge_all, color = year)) + 
                              geom_point() + geom_smooth(method = "loess", 
                                                         formula = y~x) + 
                              labs(title = "The relationship between poverty & binge_all")
```

##### For the Plot 1, there is a peak between 10 and 15, and I suppose that the peak value corresponding to the value of x-axis is 12.5.
##### 1. When poverty is less than 12.5, poverty is **proportional** to binge_all, which means that the increase in the percentage of poverty of a state, the increase in percentage of drinking prevalence among all adults;
##### 2. When poverty is between 12.5 and 35, poverty is **inversely proportional** to binge_all, which means that the increase in the percentage of poverty of a state, the decrease in the percentage of drinking prevalence among all adults;
##### 3. When binge_all is larger than 35, the curve is gradually increasing, the two variables are **proportional** again.

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2)
ggplot(data = dataset_reshape[(!is.na(dataset_reshape$binge_all)) & 
                              (!is.na(dataset_reshape$poverty)),], 
                              aes(x = binge_all, y = poverty, color = year)) + 
                              geom_point() + geom_smooth(method = "loess", 
                                                         formula = y~x) + 
                              labs(title = "The relationship between binge_all & poverty")
```

##### For the Plot 2, there is a peak between 10 and 15, and I suppose that the peak value corresponding to the value of x-axis is 13.
##### 1. When binge_all is less than 13, binge_all is **proportional** to poverty;
##### 2. When binge_all is between 13 and 20, binge_all is **inversely proportional** to poverty;
##### 3. When binge_all is larger than 20, the curve is gradually increasing, the two variables are **proportional** again.
##### **Summary: According to these two scatter plots, it can be seen that there is non-linear relationship between poverty and binge_all. Besides, the shape and movement of these two plots are roughly the same, but the curve in Plot 1 is steeper. Therefore, there may exist two-way causality relationship between the two variables.** 




##### Question 7: Calculate the average annual growth rates of overall binge drinking across states for the years the data is available. Provide a table of the 5 states with the largest increases and the 5 states with the largest decreases in binge drinking prevalence over the time period.
```{r echo = FALSE, warning = FALSE, message = FALSE}
dataset_binge_overall <- dataset_reshape[!is.na(dataset_reshape$binge_all), 
                                         c("year", "state", "binge_all")]
data_states <- arrange(group_by(dataset_binge_overall, state), year)
growth_rate <- summarise(data_states, growth_rate = 
                        (last(binge_all)-first(binge_all))*100/(5*first(binge_all)))
growth_top5 <- arrange(growth_rate, desc(growth_rate))[1:5,]
desc_top5 <- arrange(growth_rate, growth_rate)[1:5,]
```

##### **Table of 5 states with the largest increases**
```{r table 2, echo = FALSE, warning = FALSE, message = FALSE}
print(growth_top5)
```

##### **Table of 5 states with the largest decreases**
```{r table 3, echo = FALSE, warning = FALSE, message = FALSE}
print(desc_top5)
```
