---
title: "QMSS G5072 Homework 8"
author: "Mengfei Xiao"
date: "November 19th, 2018"
output: 
  html_document:
    keep_md: true
---



## Write a simple API client
### 1. Choose an API
#### a) Choose an API
I choose to use the ProPublica Congress API: It can retrieve legislative data from the House of Representatives, the Senate and the Library of Congress. 


#### b) Link to API documentation 
API documention link: https://projects.propublica.org/api-docs/congress-api/


#### c) Base URL of API
Base URL: https://api.propublica.org/congress/v1/




### 2. Authentication
#### a) How API authenticates the user
You can sign up on this website: https://www.propublica.org/datastore/api/propublica-congress-api to request an API key. After registering your name, email, organization and purpose to be a user, the website will autenticate the user.



#### b) Apply for an API key
Once registered successfully, the website will automatically send an API key for Congress API later to the user. You are required to provide more information on this website: https://www.propublica.org/datastore/api/propublica-congress-api




### 3. Send a Simple GET request
#### a) Execute a simple GET request
```{r, warning = FALSE, message = FALSE}
library(httr)
library(plyr)
library(dplyr)
library(stringr)
header <- add_headers("X-API-Key" = Sys.getenv("CONGRESS_TOKEN"))
base_URL <- "https://api.propublica.org/congress/v1/80/senate/members.json"
response <- GET(base_URL, header)
```


#### b) Check the status of the request
```{r}
http_status(response)
```


#### c) Check the type of the response
```{r}
http_type(response)
```



### 4. Parse the response and Create a dataset
#### a) and b) 
```{r}
list_data <- content(response)
result_data <- `[`(list_data, -c(1,2))
members <- list()
for(i in c(1:length(result_data$`results`[[1]]$members))){
  members[[i]] <- unlist(result_data$`results`[[1]]$members[[i]]) %>% 
    t(.) %>% 
    data.frame(.)
}
result_df <- do.call(rbind.fill, members)
result_df <- result_df[, c("id", "title", "first_name", "last_name", "gender", 
                           "date_of_birth", "party", "state", "senate_class")]
```


#### c) Provide summary statistics of the data
```{r}
summary(result_df)
saveRDS(result_df, file = "data.rds") # The "data.rds" is saved in my hw08 file #
```



### 5. API Client
#### a) Full function to access the API functionality
```{r}
getrepsentative <- function(congress = "house", number = 102, key = Sys.getenv("CONGRESS_TOKEN")){
  list_data <- list()
  result_data <- list()
  header <- add_headers("X-API-Key" = key)
  url <- str_c("https://api.propublica.org/congress/v1", number, congress, "members.json", sep = "/")
  resp <- GET(url, header)
  if(!http_status(resp)$`category`=="Success"){
    print(sprintf("%s",http_status(resp)$`message`))
  }
  if(congress=="senate" & (number<80 | number>115)){
    print(sprintf("%g out of bound script", number))
  }
  if(congress=="house" & (number<102 | number>115)){
    print(sprintf("%g out of bound script", number))
  }
  if(!congress %in% c("senate", "house")){
    print("Wrong value in congress")
  }
  list_data <- content(resp)
  result_data <- `[`(list_data, -c(1,2))
  membs<-list()
  for(i in c(1:length(result_data$`results`[[1]]$members))){
    membs[[i]] <- unlist(result_data$`results`[[1]]$members[[i]]) %>% 
      t(.) %>% 
      data.frame(.)
  }
  result_df <- do.call(rbind.fill, membs)
  return(result_df)
}
```


#### b) Save the output
```{r}
output <- getrepsentative()
saveRDS(output, file = "api_client_output.RDS") # The "api_client_output.RDS" is saved in my hw08 file #
```

