---
title: "QMSS G5072 Homework 7"
author: "Mengfei Xiao"
date: "November 8th, 2018"
output: 
  html_document:
    keep_md: true
---


## Calling an API using "httr"
```{r set up, echo = FALSE, warning = FALSE, message = FALSE}
library(httr)
library(stringr)
library(dplyr)
```

### a) Define the base URL 
```{r}
endpoint <-"https://data.lacity.org/resource/7fvc-faax.csv"
```


### b) Send a simple GET request
```{r}
str_response <- GET(endpoint, max.level = 1)
print(str_response)
```


### c) Get the content of the response
```{r, message = FALSE}
result_data <- content(str_response)
dim(result_data)
table(result_data$area_name)
```


### d) Get your access token
**Conclusion:** The status of the server response is 200, which starts with 2xx meaning that it does not have any error, and the client's request is successfully received, understood, and accepted.
```{r}
server_response <- GET(endpoint, query = list("$limit" = "10000", 
                                            "$$app_token" = Sys.getenv("LACRIME_APP_TOKEN")))
server_response$status_code
```


### e) Limiting your query
**Conclusion:** I filter the obeservations whose area_name is "Central"" and status is "double A".
```{r}
server_response_new <- GET(endpoint, query = list("$limit" = "10000", 
                                                 "$$app_token" = Sys.getenv("LACRIME_APP_TOKEN"), 
                                                 area_name = "Central", status = "AA"))
server_response_new$status_code
```


### f) Locations
```{r}
googlekey <- "AIzaSyBzubRQN0_kf0nPc_qCzM7chlX5YOf3edA"
latlng <- str_extract_all(result_data$location_1,"-?[0-9]+\\.[0-9]+") %>% 
  unlist(.)
latlng <- paste(latlng[seq(2, length(latlng), 2)], latlng[seq(1, length(latlng), 2)], sep = ",")
URL <- str_c("https://maps.googleapis.com/maps/api/geocode/json?latlng=",latlng) %>% 
  str_c(.,googlekey, sep = "&key=")
back <- list()
address <- list()
for(i in c(1:50)){
  back[[i]] <- GET(URL[i])
  if(!back[[i]]$status==200){
    print(str_c(i,"something goes awry"))
  }
  address[[i]] <- content(back[[i]])
  Sys.sleep(0.1)
}
extract_format <- function(x){
  x$results[[1]]$formatted_address
}
format_address <- lapply(address,extract_format)
format_address
```



