---
title: "QMSS G5072 Homework 9"
author: "Mengfei Xiao"
date: "November 26th, 2018"
output: 
  html_document:
    keep_md: true
---



## Web Scraping with Selectors
### 1. Get HTML
```{r warning = FALSE, message = FALSE}
library(xml2)
library(dplyr)
library(stringr)
library(rvest)
URL <- "https://en.wikipedia.org/wiki/Mitch_McConnell"
urlsrc <- read_html(URL, encoding = "UTF-8")
```



### 2. Get the info box
```{r}
infobox <- html_node(urlsrc, css = "table.infobox.vcard")
print(infobox)
```



### 3. Make a data frame
#### a) Parse the infobox table
```{r}
infodf <- html_table(infobox, fill = T, header = F)
```


#### b) Name the columns of the table
```{r results = 'hide'}
colnames(infodf) <- c("key", "value")
```


#### c) Filter the data frame
```{r}
infodf <- filter(infodf, rownames(infodf)==1|infodf$key %in% c("Political party", "Children"))
infodf[1,1] <- "Full name"
print(infodf)
```



### 4. Make a function
#### a) Output the data frame
```{r}
get_wiki_info <- function(url){
  url_source <- read_html(url, encoding = "UTF-8")
  infomation_box <- html_node(url_source, css = "table.infobox.vcard")
  infomation_df <- html_table(infomation_box, fill = T, header = F) %>% 
    `colnames<-`(.,c("key", "value"))
  infomation_df <- infomation_df[rownames(infomation_df)==1|infomation_df$key %in% 
                                   c("Political party", "Children"),]
  infomation_df[1,1] <- "Full name"
  if(!any(infomation_df$key=="Children")){
    infomation_df <- rbind(infomation_df, c("Children", NA))
  }
  return(infomation_df)
}
```


#### b) Show how your function works
```{r echo = FALSE}
get_wiki_info("https://en.wikipedia.org/wiki/Tammy_Duckworth")
get_wiki_info("https://en.wikipedia.org/wiki/Susan_Collins")
```



### 5. Get all senators’ pages
#### a) Find a list of U.S. congress
```{r echo = FALSE}
sels_url <- "https://en.wikipedia.org/wiki/List_of_current_members_of_the_United_States_Senate"
sels_src <- read_html(sels_url)
sels_link <- html_nodes(sels_src, xpath = "//table[5]//span//a") %>% 
  html_attr(.,name = "href") %>%
  str_c("https://en.wikipedia.org",.)
print(sels_link)
```


#### b) Create a loop
```{r}
res_list <- list()
for(i in seq_along(sels_link)){
  res_list[[i]] <- get_wiki_info(sels_link[i])
  Sys.sleep(0.1)
}
```


#### c) Clean up the data
```{r echo = FALSE}
res_df <- lapply(res_list,t) %>% 
  do.call(rbind,.) %>% 
  `colnames<-`(.,.[1,])
res_df <- res_df[row.names(res_df)=="value",] %>% 
  data.frame(.)
rownames(res_df) <- c(1:nrow(res_df))
index <- str_detect(res_df$Children,"[0-9]") %>% 
  ifelse(is.na(.),T,.)
res_df[!index,]$Children <- 1
res_df$Children <- str_extract(res_df$Children,"[0-9]+") %>% 
  as.numeric(.)
res_df$Political.party <- str_extract(res_df$Political.party,"[^[(]]+") %>% 
  trimws(.,"right")
res_df[res_df$Political.party=="Democratic–Farmer–Labor Party",]$Political.party <- "Democratic"
```

##### **Average children number the Senator has**
```{r echo = FALSE}
mean(res_df$Children, na.rm = T)
```


##### **Average children number the Party Affiliation have**
```{r echo = FALSE}
res_df %>%
  group_by(`Political.party`) %>%
  summarize(mean(Children, na.rm = T))
```

