---
title: "QMSS G5072 Homework 10"
author: "Mengfei Xiao"
date: "December 3rd, 2018"
output: 
  html_document:
    keep_md: true
---



## Practicing SQL Queries
```{r set up, echo = FALSE, message = FALSE, warning = FALSE}
# Connect to the database
library(DBI)
witch_con <- dbConnect(RMySQL::MySQL(),
                       user='student', 
                       password='mds-is-fun',
                       dbname='witchcraft', 
                       host='tbrambor.cczjcoy6i2jn.us-east-1.rds.amazonaws.com',
                       port = 3306)
```


### 1. Getting to know the data
#### a) Show a list of the tables included in the database
```{r message = FALSE, warning = FALSE}
table_list <- dbListTables(witch_con)
table_list
```


#### b) Display the column names for the table accused
```{r message = FALSE, warning = FALSE}
table_accused <- dbReadTable(witch_con, "accused")
colnames(table_accused)
```


#### c) Number of people included in the accused table
```{r message = FALSE, warning = FALSE}
nrow(table_accused)
```


#### d) Display the columns firstname, sex, and age for 5 cases
```{r message = FALSE, warning = FALSE}
dbGetQuery(witch_con, "select firstname, sex, age from accused limit 5")
```


#### e) Count the number of nonmissing values for age
```{r echo = FALSE, message = FALSE, warning = FALSE}
dbGetQuery(witch_con, "select count(*) from accused where age is not null")
```


#### f) Show a list of unique occupations
```{r message = FALSE, warning = FALSE}
dbGetQuery(witch_con, "select distinct occupation from accused")
```



### 2. Seeing the Devil
#### a) List the unique devil_types in the data
```{r message = FALSE, warning = FALSE}
dbGetQuery(witch_con, "select distinct devil_type from devilappearance")
```


#### b) Number of sightings mention the word "black"
```{r message = FALSE, warning = FALSE}
dbGetQuery(witch_con, "SELECT count(*) FROM devilappearance where devil_text like '%black%'")
```


#### c) Proportion of the devils are male
```{r message = FALSE, warning = FALSE}
male_count <-  dbGetQuery(witch_con, "select sum(devil_type = 'Male') from devilappearance")
all_count <- dbGetQuery(witch_con, "select count(devil_type) from devilappearance")
male_count$`sum(devil_type = 'Male')`[1]/all_count$`count(devil_type)`[1]
```



### 3. The Trial
#### a) Average and Maximum numbers of male and female accusers
```{r message = FALSE, warning = FALSE}
dbGetQuery(witch_con, "select max(male_accusers), avg(male_accusers), 
           max(female_accusers), avg(female_accusers) from trial")
```


#### b) List the number of sentences by sentence typeist in a table
```{r message = FALSE, warning = FALSE}
dbGetQuery(witch_con, "select sentence as 'sentence_type', count(sentence) as 'Freq'
           from trial group by sentence order by count(sentence) desc")
```


#### c) Compare the average number of accusers by the type of verdict
```{r message = FALSE, warning = FALSE}
dbGetQuery(witch_con, "select verdict as 'verdict_type', avg(male_accusers+female_accusers) as 
           'Average accusers' from trial where verdict<>'' group by verdict order by 
           avg(male_accusers+female_accusers) desc")
```


### 4. Tortured Truth
#### a) Left join the trial and confession tables
```{r message = FALSE, warning = FALSE}
dbGetQuery(witch_con, "SELECT count(distinct(confession.confessionref)) as 'Number_of_Confession', 
           count(distinct(trial.trialref)) as 'Number_of_Trial', 
           count(distinct(confession.confessionref))/count(distinct(trial.trialref)) 
           as 'Share_of_Trial_with_confession' 
           FROM trial LEFT JOIN confession ON trial.trialref = confession.trialref")
```


#### b)
**Conclusion:** Only 110 of trials have records of torture, and among of which have 35 confessions. Therefore, there is a higher share of confessions among trials with records of torture than trials without such record since the share is 0.3182, larger than 0.2931 in Quesion 4a).
```{r message = FALSE, warning = FALSE}
dbGetQuery(witch_con, "select count(distinct(torture.tortureref)) as 'Number_of_Torture', 
           count(distinct(confession.confessionref)) as 'Number_of_Torture_with_Confession', 
           count(distinct(confession.confessionref))/count(distinct(torture.tortureref))
           as 'Share_of_Torture_with_Confession' 
           FROM torture left join confession on torture.trialref = confession.trialref")
```
```

